Precise Weed and Maize Classification through Convolutional Neuronal Networks

### 2017-08-17 PaperBCJ.tex
Corrections of Review 2

Also, the use of Linux OS in the development stages was important due to its light operating system and free OS which is also fully compatible with OpenCV. The computer used in the project worked with Ubuntu Linux 16.04 due to its official support to CUDA, Caffe and OpenCV. Likewise, Pixel OS was used in Raspberry Pi for acquiring images and testing the CNN classification performance.
\\

@@

Due to the lack of local weed and maize plants datasets, it was necessary to search for maize crops. The initial development stage of maize was selected because actions taken by the farmer during this stage are easier to execute and these will impact the future crop yield. Fieldwork at a nearby town called P\'illaro was arranged with the purpose of obtaining image samples. P\'illaro is a city located in the Tungurahua Province, in the center of the Ecuadorian Highlands region, it is a recognized andean-crop producer of species such as maize, potatoes and a wide variety of fruits. Due to its year-long production season, many maize crops at its initial development stage were found in this area. \\

@@

\begin{comment}	
En el caso de querer implementar el algoritmo en un sitema embedded, no se recomienda trabajar con procesador como el de la Rasp Berry Pi 3, pues tiene un procesamiento muy lento debido a que los frames por segundo necesario para analizar las imagenes es significativamente bajo, por lo que se debera elegir una targeta que disponga de GPU, sin necesidad del uso de Multithreading y Batching. 
\end{comment}

>>>>

Also, the use of Linux OS in the development stages was important due to its light operating system and free OS which is also fully compatible with OpenCV. The computer used in the project worked with Ubuntu Linux 16.04 due to its official support to CUDA, Caffe and OpenCV. Likewise, PIXEL Distribution derived from Debian Linux was used in Raspberry Pi for acquiring images and testing the CNN classification performance.
\\

@@

Due to the lack of local weed and maize plants datasets, it was necessary to search for those classes of plants in maize crops. The initial development stage of maize was selected because actions taken by the farmer during this stage are easier to execute and these will impact the future crop yield. Fieldwork at a nearby town called P\'illaro was arranged with the purpose of obtaining image samples. P\'illaro is a city located in the Tungurahua Province, in the center of the Ecuadorian Highlands region, it is a recognized andean-crop producer of species such as maize, potatoes and a wide variety of fruits. Due to its year-long production season, many maize crops at its initial development stage were found in this area. \\

@@

\begin{comment}	
En el caso de querer implementar el algoritmo en un sitema embedded, no se recomienda trabajar con procesador como el de la Raspberry Pi 3, pues tiene un procesamiento muy lento debido a que los frames por segundo necesario para analizar las imagenes es significativamente bajo, por lo que se debera elegir una targeta que disponga de GPU, sin necesidad del uso de Multithreading y Batching. 
\end{comment}
